---
title: "cw-vector-map-1"
author: "Jared 'Jay' Klein"
date: "1/26/2022"
output: word_document
---

```{r}
library(tidyverse)
library(dplyr)
```


```{r}
V <- c("Bears", "Lions", "Dolphins", "Eagles", "Bengals")
```

1) Why is the vector shown above an atomic vector? (Explain using two or three sentences)
_The above vector is an atomic vector because it contains objects of the same type. They are all strings._

2) Use and show R code that will extract "Dolphins" from the vector shown above.
```{r}
V[3]
```


3) Use and show Rcode that will extract "Bears" , "Dolphins" and 
"Bengals" from the vector shown above.
```{r}
V[c(1, 3, 5)]
```


4) Use and show two Rcoding methods that will show all objects of the vector given above except "Bears".
```{r}
V[-1]
V[V != "Bears"]
```

+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
```{r}
K <- list( x = 3:7, "never", 43, y = list(10,20,30))
```

5) Why is the vector given above called a list? (Explain in two or three sentences) If the vector is a list, identify the type of each object in the list.
_The vector specified as K above the question is considered a list because it contains objects of different R data types. The list, "K", has a sequence integer, a string, an integer, and a list. _

6) Use and show R code that will give the length of the vector shown above.
```{r}
length(K)
```

7) Use and show R code that will output the fourth object in the vector shown above.
```{r}
K[4]
```

8) Use and show R code that will show all objects in the vector (list) given above.
```{r}
K
```

9) Copy paste and run the tribble given below.
tribble( ~x,    ~y,    ~w,    ~z,
              210,   300,   220,   180,
              102,   100,   119,   187,
              176,   175,   188,   173,
              87,    95,   91,     94,
              202,   210,  234,    218,
              110,   122,  131,    128,
) -> dt
dt
```{r}
tribble( ~x,    ~y,    ~w,    ~z,
              210,   300,   220,   180,
              102,   100,   119,   187,
              176,   175,   188,   173,
              87,    95,   91,     94,
              202,   210,  234,    218,
              110,   122,  131,    128,
) -> dt
dt
```

9a) Use and show a map function to find the mean of each column of the dt data table
```{r}
map_dbl(dt, mean)
```

9b) Use and show a map function to find the standard deviation of 
each column of the dt data table.
```{r}
map_dbl(dt, sd)
```

9c) Use and show a map function that will calculate the square root
of each value of each column of the data table dt.
```{r}
dt %>%  
  map(~. ^ 1/2)
```


9d) Use R code to find the mean, max, 1st Quartile, 2nd Quartile,
Median, and Mean for each column of the dt data table. (Hint: You do
not have to use a map function)
```{r}
summary(dt)
```

Professor said skip #10