---
title: "cw-funcs-1"
author: "Jared 'Jay' Klein"
date: "1/19/2022"
output: word_document
---

```{r}
library(tidyverse)
```

## 1. __In three or four sentences explain why constructing a function, in order to execute tasks is beneficial or advantageous__

There are a number of reasons as to why you would need to use functions. First, off, it's just good programming especially when utilizing/building objects in most languages. Functions are the key to clean, modular code and different activities/tasks a program executes should be kept in their own functions so you can better debug programs later. Also, they are useful for repeating tasks within a code base. 

## 2. __Write a function (using r code and structure demonstrated in class) to calculate a z-score for a given observed value, a mean, and a standard deviation value. And then use our function to find a z score for the following problem.  Observed_value = 25.77, mean = 23.54, standard deviation = 2.442__

```{r}
z_score_func <- function(obv, mean, std) {
  score <- (obv - mean) / (std)
  return(score)
}

z_score_func(25.77, 23.54, 2.442)
```

## 3. __Write a function to calculate the natural log fo a number multiplied by the common log of the same number divided by the cube root of a given prime number, round to the nearest tenth. Use your function to find the answer if the number to be used for both log expressions is 32 and the given prime number is 11.__

```{r}
some_func <- function(nm, prm_nm){
  output_value <- (log(nm)*log10(nm))/(prm_nm^(1/3))
  return(round(output_value, digits = 1))
}

some_func(32, 11)
```

## 4. __Use and show R coding to calculate the standard deviation for each variable of the data table mtcars using the "Special For Loop Method" demonstrated in the class notes.__
```{r}
?mtcars
```


```{r}
some_std_func <- function() {
  for (variable in mtcars) {
    print(sd(variable))
  }
}

some_std_func()

## checking work: 
print("The first and last output of the function above should match the two below: ")
sd(mtcars$mpg)
sd(mtcars$carb)
```

