---
title: "cw-map2maploop-1"
author: "Jared 'Jay' Klein"
date: "2/2/2022"
output: word_document
---

```{r}
library(tidyverse)
```


```{r}
x <- list(2, 4, 5, 9, 1)
y <- list(8, 7, 2, 8, 3)
z <- list(1, 8, 5, 4, 2)
```

1) __For the lists given above, show and use R code (a map function) to iteratively find the square of the sums across the vectors__

```{r}
pmap_dbl(list(x,y,z), function(first, second, third) (first + second + third)^2)
```

tribble( ~Student,  ~Gender,    ~Salary,
                   "John",   "Male",       65000,
                   "Alice",  "Female",    73000,
                    "Juan",   "Male",       66000,
                    "Beth",  "Female",    71500,
                    "Denise", "Female",  82000
) -> table
table
2) __Using the data table above, use and show R code that will output a statement that is descriptive for all rows of the data table.The first row is given below.  Your code should produce the other specific statements. _John who is Male, has a salary that is 65000 dollars per year_.__
```{r}
tribble( ~Student,  ~Gender,    ~Salary,
                   "John",   "Male",       65000,
                   "Alice",  "Female",    73000,
                    "Juan",   "Male",       66000,
                    "Beth",  "Female",    71500,
                    "Denise", "Female",  82000
) -> table
```
```{r}
table %>%
  pmap_chr(~ str_glue("{..1} who is {..2} has a salary that is {..3} per year."))
```

3) __Write a nested loop that will produce a 5 by 5 matrix that whose matrix elements are sums of the corresponding columns and rows.__
```{r}
da_matrix1_was_da_best_movie = matrix(nrow = 5, ncol = 5)
for (variable in 1:nrow(da_matrix1_was_da_best_movie)) {
  for (var in 1:ncol(da_matrix1_was_da_best_movie)) {
    da_matrix1_was_da_best_movie[variable,var] = variable + var
  }
}
print(da_matrix1_was_da_best_movie)
```


4) Use for loop coding to produce the number sequence
```{r}
i <- 1
while(i < 21){
  if (i == 10 | i == 5) {
    i = i + 1
    next
  } else {
    print(i)
    i = i + 1
  }
}
```

