---
title: "Classwork Datetime 1"
author: "Jared 'Jay' Klein"
date: "1/12/2022"
output: word_document
---
```{r}
library(tidyverse)
library(nycflights13)
library(lubridate) 
library(dplyr)
```


1) Use and show R code to extract the month from the following datetime 
designation;
datetime2 <- ymd_hms("2021-11-13 10:05:31")
datetime2
```{r}
datetime2 <- ymd_hms("2021-11-13 10:05:31")
month(datetime2)
```

2) Use and show R code to extract the day of the week from the following 
datetime designation;
```{r}
datetime2 <- ymd_hms("2021-11-13 10:05:31")
day(datetime2)
```
3) Use and show R code to change the month to 8, and the hour to 5 for the 
following datetime designation
datetime2 <- ymd_hms("2021-11-13 10:05:31")
datetime2
```{r}
datetime2 <- ymd_hms("2021-11-13 10:05:31")
update(datetime2, month = 8, hour = 5)
```

4) Use and show R code to change 6 hours to seconds.
```{r}
dhours(6)
```

5) Use and show R code to change 4 days to seconds.
```{r}
ddays(4)
```

6) Use and show R code to add 7years to 30 days.
```{r}
years(7) + days(30)
```

7 Use and show R code to determine how many weeks there are from today's 
date to a year from now.
```{r}
next_year <- today() + years(1)
(today() %--% next_year)%/%dweeks(1)
```

8) Use and show R code to determine how many days there are between today's 
date and June 28, 2022.
```{r}
(today() %--% mdy("06-28-2022"))%/%ddays(1)
```
