---
title: "hw-dates-time"
author: "Jared 'Jay' Klein"
date: "1/17/2022"
output: word_document
---

```{r}
library(tidyverse)
library(nycflights13)
library(lubridate)  
library(dplyr)
```


## *1) Use and show R coding to find the number of days from June 6th 2020 to July 14th 2021*
```{r}
(mdy("06-06-2020") %--% mdy("08-14-2021"))%/%ddays(1)
```


## *2) Use and show R coding to confirm that the year 1988 was a leap year.*
```{r}
leap_year(1988)
```


## *3) Use and show R coding to confirm that the year 1989 was not a leap year.*
```{r}
leap_year(1989)
```


## *4)  Why is there months() but no dmonths ? (Answer in 3 to four sentences)*
Days in a month are ambiguous. For example, February can have 28 to 29 days depending on the year. Furthermore, a month is the recording of time between two dates rather than a set period of time.

## *5)  John was born April 11th, 1962. Use and show R coding to determine how old John is in years*
```{r}
b_day_john <- mdy("04-11-1962")
(b_day_john %--% today())%/%dyears(1)
```


## *6) Modify the flights_dt coding in the notes or the book to obtain the following partial data table shown below.  Show all required coding. (Most of the coding needed is provided in the notes)*
```{r}

make_datetime_100 <- function(year, month, day, time) {
  make_datetime(year, month, day, time %/% 100, time %% 100)
}

flights %>% 
  filter(!is.na(dep_time), !is.na(arr_time)) %>% 
  mutate(
    dep_time = make_datetime_100(year, month, day, dep_time),
    arr_time = make_datetime_100(year, month, day, arr_time),
    sched_dep_time = make_datetime_100(year, month, day, sched_dep_time),
    sched_arr_time = make_datetime_100(year, month, day, sched_arr_time)
  ) %>% 
  select(origin, dest, carrier, arr_time, dep_time) -> flights_dt

flights_dt
  
  
```
__PLEASE NOTE THAT THE TABLE SHOWN IN THE ASSIGNMENT DOCUMENT ONLY SHOWS 4 COLUMNS BUT IS MARKED AS A TIBBLE WITH 5 COLUMNS INSTEAD. I HAVE INCLUDED "dep_time" AS A CAUTION__ 

## *7) Now, using your table from #6, produce the frequency plot shown which conveys frequency counts for the months of April, July, and October for the year 2013*
```{r}
flights_dt %>%
  filter(between(as_date(arr_time), as_date("2013-04-01"), as_date("2013-10-01")))%>%
  ggplot(aes(arr_time)) + 
  geom_freqpoly(binwidth = ddays(1))
```


## *8) Now use dplyr functions to produce a data table that shows arrival times for American Airlines at the Dallas Fort Worth Airport from the LaGuardia airport in New York. Your output should show rows 115 to 125.*
```{r}
flights_dt %>%
  select(origin, dest, carrier, arr_time)%>%
  filter(origin == "LGA", dest == "DFW", carrier=="AA") %>%
  slice(115:125) -> aa_lga_to_dfw

aa_lga_to_dfw
```


## *9) Using the first two observational date time designations from your #8 table, Use and show R code to confirm that there are 181 minutes time intervals between them.*
```{r}
aa_lga_to_dfw %>%
  slice(1:2)%>%
  select(arr_time)%>%
  mutate(minute_interval = (lag(arr_time) %--% arr_time%/%dminutes(1)))
```

